Comparing probabilistic predictive models applied to football

### 2015-06-26 template.tex
intoducao de secao benchmark models

In this section we present the probabilistic justification for the
three proposed models and the predictive distribution of an upcoming
match of team $A$ (home team) versus $B$ (away team). The main idea
is to combine the past performance of both teams in different ways
in order to predict the outcome of the match. The predictions of the
two benchmark models were published before each matchday at
\url{http://chancedegol.uol.com.br} and
\url{http://www.previsaoesportiva.com.br}.

@@

\subsection{Model 3: Multinomial-Dirichlet 3}
\label{sec::Mn_Dir3}

@@

\bibitem{Crowder2002} Crowder, M.; Dixon, M.; Ledford, A.; Robinson, M. Dynamic modelling and prediction of English
Football League matches for betting {\em Journal of the Royal
Statistical Society - Series D} {\bf 2002}, {\em 51}, 157-168.

@@

\bibitem{McHale2011}
McHale, I.; Scarf, P. Modelling the dependence of goals scored by
opposing teams in international soccer matches. {\em Statistical
Modelling} {\bf 2011}, {\em 11}, 219–236.

@@

\bibitem{Rue2000}
Rue, H.; Salvesen, O. Prediction and Retrospective Analysis of
Soccer Matches in a League {\em Journal of the Royal Statistical
Society - Series D} {\bf 2000}, {\em 49}, 399-418.

>>>>

In this section, we present the basic assumptions adopted by the benchmark models and 
by the three proposed models. The predictions of the
two benchmark models were published before each matchday at
\url{http://chancedegol.uol.com.br} and
\url{http://www.previsaoesportiva.com.br}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Benchmark Models}
\label{sec::Benchmark}

@@

\subsection{Model Three: Multinomial-Dirichlet 3}
\label{sec::Mn_Dir3}

@@

\bibitem{Crowder2002} Crowder, M.; Dixon, M.; Ledford, A.; Robinson, M. Dynamic modelling and prediction of English
Football League matches for betting. {\em Journal of the Royal
Statistical Society - Series D} {\bf 2002}, {\em 51}, 157-168.

@@

\bibitem{McHale2011}
McHale, I.; Scarf, P. Modelling the dependence of goals scored by
opposing teams in international soccer matches. {\em Statistical
Modelling} {\bf 2011}, {\em 11}, 219-236.

@@

\bibitem{Rue2000}
Rue, H.; Salvesen, O. Prediction and Retrospective Analysis of
Soccer Matches in a League. {\em Journal of the Royal Statistical
Society - Series D} {\bf 2000}, {\em 49}, 399-418.
